---

title: "sample_sheet_rmd_ID"
output: html_document
---

import tidyverse 
```{r} 
library(tidyverse)
```


Optional step: clean out variables in global env from previous runs
```{r}
rm(BioSample_Description,BioSample_ID,date2,FACS_Markers, final_update,Gender,Host,index,Sample_ID,Organism,input,index_subset,Sample_Owner,sequencer,Study_Description,Study_ID,Tissue_Source,update_index_subset)
```


Choose a sequencer: miseq, nextseq, novaseq
```{r}
sequencer <- "novaseq"
```

These values will be the same for the entire column of sample sheet
```{r}
Study_ID <- "AIH"
Study_Description <- "Evaluation of host differential gene expression in patients with autoimmune hepatitis"
BioSample_ID <- "AIH-BLD-RNA"
BioSample_Description <- "Peripheral blood"
Sample_ID <- c()
Sample_Owner <- "Amy_Lyden"
Organism <- "Human"
Host <- "Human"
Gender <- ""
Tissue_Source <- ""
FACS_Markers <- ""
```

Please specify correct input and index files (specify path if not in same wd)
```{r}
index <- read_csv(file = "2018_CAT_Novaseq_Barcodes_All.csv")
input <- read_csv("OPool_0034.csv")
```


No changes beyond this point. This part of the code will extract the correct barcodes from the index file, use the correct i5 index (i5 or revcom), then fill in the rest of the sample sheet with given information. Output will be a file with today's date.
```{r}
index$index_name <- paste(index$index_plate,"_",index$well, sep="")
input$index_name <- paste(input$`Barcode Plate`,"_",input$`Barcode Well`, sep="")
index_subset <- subset(index, index_name %in% input$index_name)

if (sequencer == "novaseq" ||
    sequencer == "miseq") {
  update_index_subset <- index_subset %>%
    select(
      Index_ID = index_name,
      Index = i7,
      Index2 = `i5-revcomp`,
      well,
      index_plate
    )
} else {
  update_index_subset <- index_subset %>%
    select(
      Index_ID = index_name,
      Index = i7,
      Index2 = i5,
      well,
      index_plate
    )
}

update_index_subset$Sample_Name <-
  input$Sample_ID[match(update_index_subset$Index_ID, input$index_name)]

final_update <- update_index_subset %>%
  add_column(
    Study_ID,
    Study_Description,
    BioSample_Description,
    BioSample_ID,
    Sample_Owner,
    Sample_ID = update_index_subset$Sample_Name,
    Index2_ID = update_index_subset$Index_ID,
    Organism,
    Host,
    Gender,
    Tissue_Source,
    FACS_Markers
  ) %>%
  select(
    Study_ID,
    Study_Description,
    BioSample_ID,
    BioSample_Description,
    Sample_ID,
    Sample_Name,
    Sample_Owner,
    Index_ID,
    Index,
    Index2_ID,
    Index2,
    Organism,
    Host,
    Gender,
    Tissue_Source,
    FACS_Markers
  )


date2 <- Sys.Date()
write_csv(final_update, paste(date2, "_", Study_ID, "_sample_sheet.csv", sep = ""))


```