---

title: "sample_sheet_rmd_ID"
output: html_document
---

import tidyverse 
```{r} 
library(tidyverse)
```


Optional step: clean out variables in global env from previous runs
```{r}
rm(BioSample_Description,BioSample_ID,date2,FACS_Markers, final_update,Gender,Host,index,Sample_ID,Organism,input,index_subset,Sample_Owner,sequencer,Study_Description,Study_ID,Tissue_Source,update_index_subset)
```


Choose a sequencer: miseq, nextseq, novaseq
```{r}
sequencer <- "novaseq"
```

These values will be the same for the entire column of sample sheet
```{r}
Study_ID <- "TB-FLASH"
Study_Description <- "CSF DNA seq of patients with TB/HIV co-infection as controls for future FLASHed samples"
BioSample_ID <- "TB-FLASH-CSF-DNA"
BioSample_Description <- "Cerebrospinal fluid"
Sample_ID <- c()
Sample_Owner <- "Amy_Lyden"
Organism <- "mycobacterium tuberculosis"
Host <- "human"
Gender <- ""
Tissue_Source <- ""
FACS_Markers <- ""
```

Please specify correct input and index files (specify path if not in same wd)
```{r}
i7 <- read_csv(file = "CZB_TruSeq_12BP_i7.csv")
i5 <- read_csv(file = "CZB_TruSeq_12BP_i5.csv")
input <- read_csv("OPool_0035.csv")
output <- " "

```


No changes beyond this point. This part of the code will extract the correct barcodes from the index file, use the correct i5 index (i5 or revcom), then fill in the rest of the sample sheet with given information. Output will be a file with today's date.
```{r}
i7$index_name <- paste(i7$'Indexing Plate Name',"_",i7$Well, sep="")
i5$index_name <- paste(i5$'Indexing Plate Name',"_",i5$Well, sep="")

input$i7_name <- paste(input$`i7 index`,"_",input$`Barcode Well`, sep="")
input$i5_name <- paste(input$`i5 index`,"_",input$`Barcode Well`, sep="")

index_subset_i7 <- subset(i7, index_name %in% input$i7_name)
index_subset_i5 <- subset(i5, index_name %in% input$i5_name)
index_subset <- cbind.data.frame(index_subset_i5, index_subset_i7)
?cbind.data.frame

if (sequencer == "novaseq" ||
    sequencer == "miseq") {
  update_index_subset <- data.frame(
      Index_ID = index_subset_i7$index_name,
      Index2_ID = index_subset_i5$index_name,
      Index = index_subset_i7$`RevComp index`,
      Index2 = index_subset_i5$`RevComp Index`,
      well = input$`Barcode Well`,
      Sample_ID = input$Sample_ID
    )
} else {
  update_index_subset <- data.frame(
      Index_ID = index_subset_i7$index_name,
      Index2_ID = index_subset_i5$index_name,
      Index = index_subset_i7$`RevComp index`,
      Index2 = index_subset_i5$`Forward index`,
      well = input$`Barcode Well`,
      Sample_ID = input$Sample_ID
    )
}

update_index_subset$Sample_ID <-
  input$Sample_ID[match(update_index_subset$Index_ID, input$i7_name)]

final_update <- update_index_subset %>%
  add_column(
    Study_ID,
    Study_Description,
    BioSample_Description,
    BioSample_ID,
    Sample_Owner,
    Sample_Name = update_index_subset$Sample_ID,
    Organism,
    Host,
    Gender,
    Tissue_Source,
    FACS_Markers
  ) %>%
  select(
    Study_ID,
    Study_Description,
    BioSample_ID,
    BioSample_Description,
    Sample_ID,
    Sample_Name,
    Sample_Owner,
    Index_ID,
    Index,
    Index2_ID,
    Index2,
    Organism,
    Host,
    Gender,
    Tissue_Source,
    FACS_Markers
  )


date2 <- Sys.Date()
time <- str_split(Sys.time(), " ")
write_csv(final_update, paste(date2, "_", output, "_sample_sheet.csv", sep = ""))


```